quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Updated table

Add a table of data sets that quollr have

@@

This function requires several parameters: the high-dimensional data (`highd_data`), the emdedding data (`nldr_data`), the number of bins along the x-axis (`bin1`), the buffer amount as a proportion of data (`q`), and benchmark value to extract high density hexagons (`benchmark_highdens`). The function returns an object that includes the hexagonal object, the fitted model in both $2\text{-}D$, and $p\text{-}D$, and triangular mesh.

>>>>

The `quollr` package comes with several data sets that load with the package. These are described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:datasets-tb-html)', '\\@ref(tab:datasets-tb-pdf)'))`.

```{r}
datasets_tb <- tibble(dt = c("scurve",
                             "scurve_umap",
                             "scurve_umap_predict",
                             "scurve_umap2",
                             "scurve_umap3",
                             "scurve_umap4",
                             "scurve_umap5",
                             "scurve_umap6",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"), 
                      text = c("Simulated data to generate a S-curve with additional noise dimensions.",
                             "The UMAP embedding with n_neighbors $46$ and min_dist $0.9$ for `S-curve`.",
                             "scurve_umap_predict",
                             "The UMAP embedding with n_neighbors $10$ and min_dist $0.4$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $62$ and min_dist $0.1$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $30$ and min_dist $0.5$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $15$ and min_dist $0.5$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $15$ and min_dist $0.1$ for `S-curve`.",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"))
```

```{r datasets-tb-html, eval=knitr::is_html_output()}
datasets_tb |> 
  kable(caption = "quollr data sets", col.names = c("data", "explanation")) 
```

```{r datasets-tb-pdf, eval=knitr::is_latex_output()}
datasets_tb |> 
  kable(caption = "quollr data sets", format="latex", col.names = c("data", "explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

This function requires several parameters: the high-dimensional data (`highd_data`), the emdedding data (`nldr_data`), the number of bins along the x-axis (`bin1`), the buffer amount as a proportion of data (`q`), and benchmark value to extract high density hexagons (`benchmark_highdens`). The function returns an object that includes the scaled NLDR object (`nldr_obj`), the hexagonal object (`hb_obj`), the fitted model in both $2\text{-}D$ (`model_2d`), and $p\text{-}D$ (`model_highd`), and triangular mesh (`trimesh_data`).

### 2025-05-12 paper-quollr.tex
Updated table

\caption{\label{tab:datasets-tb-pdf}cquollr data sets}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
data & explanation\\
\midrule
scurve & scurve\\
scurve\_umap & scurve\_umap\\
scurve\_umap\_predict & scurve\_umap\_predict\\
scurve\_umap2 & scurve\_umap2\\
scurve\_umap3 & scurve\_umap3\\
\addlinespace
scurve\_umap4 & scurve\_umap4\\
scurve\_umap5 & scurve\_umap5\\
scurve\_umap6 & scurve\_umap6\\
scurve\_model\_obj & scurve\_model\_obj\\
scurve\_umap\_mse & scurve\_umap\_mse\\
\addlinespace
scurve\_umap\_mse2 & scurve\_umap\_mse2\\
scurve\_umap\_mse3 & scurve\_umap\_mse3\\
scurve\_umap\_mse4 & scurve\_umap\_mse4\\
scurve\_umap\_mse5 & scurve\_umap\_mse5\\
scurve\_umap\_mse6 & scurve\_umap\_mse6\\
\bottomrule
\end{tabular}
\end{table}

@@

This function requires several parameters: the high-dimensional data (\texttt{highd\_data}), the emdedding data (\texttt{nldr\_data}), the number of bins along the x-axis (\texttt{bin1}), the buffer amount as a proportion of data (\texttt{q}), and benchmark value to extract high density hexagons (\texttt{benchmark\_highdens}). The function returns an object that includes the hexagonal object, the fitted model in both \(2\text{-}D\), and \(p\text{-}D\), and triangular mesh.

>>>>

\caption{\label{tab:datasets-tb-pdf}quollr data sets}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
data & explanation\\
\midrule
scurve & Simulated data to generate a S-curve with additional noise dimensions.\\
scurve\_umap & The UMAP embedding with n\_neighbors \$46\$ and min\_dist \$0.9\$ for `S-curve`.\\
scurve\_umap\_predict & scurve\_umap\_predict\\
scurve\_umap2 & The UMAP embedding with n\_neighbors \$10\$ and min\_dist \$0.4\$ for `S-curve`.\\
scurve\_umap3 & The UMAP embedding with n\_neighbors \$62\$ and min\_dist \$0.1\$ for `S-curve`.\\
\addlinespace
scurve\_umap4 & The UMAP embedding with n\_neighbors \$30\$ and min\_dist \$0.5\$ for `S-curve`.\\
scurve\_umap5 & The UMAP embedding with n\_neighbors \$15\$ and min\_dist \$0.5\$ for `S-curve`.\\
scurve\_umap6 & The UMAP embedding with n\_neighbors \$15\$ and min\_dist \$0.1\$ for `S-curve`.\\
scurve\_model\_obj & scurve\_model\_obj\\
scurve\_umap\_mse & scurve\_umap\_mse\\
\addlinespace
scurve\_umap\_mse2 & scurve\_umap\_mse2\\
scurve\_umap\_mse3 & scurve\_umap\_mse3\\
scurve\_umap\_mse4 & scurve\_umap\_mse4\\
scurve\_umap\_mse5 & scurve\_umap\_mse5\\
scurve\_umap\_mse6 & scurve\_umap\_mse6\\
\bottomrule
\end{tabular}
\end{table}

@@

This function requires several parameters: the high-dimensional data (\texttt{highd\_data}), the emdedding data (\texttt{nldr\_data}), the number of bins along the x-axis (\texttt{bin1}), the buffer amount as a proportion of data (\texttt{q}), and benchmark value to extract high density hexagons (\texttt{benchmark\_highdens}). The function returns an object that includes the scaled NLDR object (\texttt{nldr\_obj}), the hexagonal object (\texttt{hb\_obj}), the fitted model in both \(2\text{-}D\) (\texttt{model\_2d}), and \(p\text{-}D\) (\texttt{model\_highd}), and triangular mesh (\texttt{trimesh\_data}).
